General exp analysis -- 4/18/2018

### 2018-11-01 resistingrhythm/analysis/paper_figures_v3.Rmd
Tweak v3

# -----------------------------------------------------------------------
# 15: Sustained E, with H
exp_code <- 201
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
stim_codes <- c(3)#, 4)

@@

# -----------------------------------------------------------------------
# 22: Sustained E, with NO H
exp_code <- 200
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
stim_codes <- c(3) #, 3)

@@

# -----------------------------------------------------------------------
# Calcium exp, E, sustained
exp_code <- 19
osc_codes <- c(105, 115, 125, 135, 145, 155)
osc_rates <- c(0.5, 1.5, 2.5, 3.5, 4.5, 5.5)
stim_codes <- c(0, 1)

@@

results19 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    for(ca in ca_targets){
      o_c <- osc_codes[i]
      o_r <- osc_rates[i]

@@

      results19 <- rbind(results19, df)
    }
  }
}

# -----------------------------------------------------------------------
# Add default Ca value, from exp
exp_code <- 15
osc_codes <- c(105, 115, 125, 135, 145, 155)
osc_rates <- c(0.5, 1.5, 2.5, 3.5, 4.5, 5.5)
stim_codes <- c(0, 1)
ca_targets <- c(0.03, 0.03, 0.03, 0.03)

for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    for(ca in ca_targets){

@@

      results19 <- rbind(results19, df)
    }
  }
}

@@

results200 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(mse_error), SD=sd(mse_error)) -> tmp2

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=mse_error, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8) +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), width=.15, size=0.2) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(title="a.", y="Variance (s)", x="Osc. rate (Hz)") +
  # # lims(y=c(0, .15)) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.35, size=18, face="bold")) -> p1

@@

results201 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(mse_error), SD=sd(mse_error)) -> tmp2

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=mse_error, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8) +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), width=.15, size=0.2) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(title="b.", y="Variance (s)", x="Osc. rate (Hz)") +
  # lims(y=c(0, .01)) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.5, size=18, face="bold")) -> p2

@@

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k - rate_ref, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8) +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), width=.15, size=0.2) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(title="d.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
  # lims(y=c(0, 70)) +
  geom_hline(yintercept=0, size=0.2) +
  theme_classic() + 
  theme(plot.title = element_text(hjust = -.25, size=18, face="bold")) -> p3

@@

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k - rate_ref, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8) +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), width=.15, size=0.2) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(title="e.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
  # lims(y=c(-4, 4)) +
  geom_hline(yintercept=0, size=0.2) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.3, size=18, face="bold")) -> p4

@@

results204 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(mse_error), SD=sd(mse_error)) -> tmp2

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=mse_error, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05), color="dodgerblue3") +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8, color="dodgerblue3") +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), 
                width=.15, size=0.2, color="dodgerblue3") +
  labs(title="c.", y="Variance (s)", x="Osc. rate (Hz)") +
  theme_classic() + 
  # lims(y=c(0, .01)) +
  theme(plot.title = element_text(hjust = -.6, size=18, face="bold")) -> p5

@@

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k - rate_ref, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05), color="dodgerblue3") +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.6, color="dodgerblue3") +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), 
                width=.15, size=0.2, color="dodgerblue3") +
  geom_hline(yintercept=0, size=0.2) +
  labs(title="d.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
  # lims(y=c(-3, 3)) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.4, size=18, face="bold")) -> p6

@@

tmp5 <- rbind(tmp3, tmp4)
tmp5 %>% 
  ggplot(aes(x=osc_mode, y=rate_k - rate_ref, color=osc_mode)) +
  geom_point(size=-1, aes(fill=osc_mode)) +
  geom_boxplot(notch = TRUE, width=0.4,  outlier.size=0.05, outlier.alpha=0.5, show.legend=FALSE) +
  labs(title="f.", y=expression(Delta*" rate (Hz)"), x="") +
  theme_classic() +
  geom_hline(yintercept=0, size=0.2) +
  # lims(y=c(-3, 3)) +
  scale_fill_manual(values=c("dodgerblue3", "black"), name="Oscillation") +
  scale_color_manual(values=c("dodgerblue3", "black"), name="Oscillation") +
  stat_compare_means(method="wilcox.test", label="p.signif", 
                     label.x=1.3, size=3, show.legend=FALSE) +
  guides(fill = guide_legend(override.aes = list(shape = 15, size = 7, alpha=0.8))) +
  theme(
    legend.position = c(0.1, 2),
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.5, "cm"),
    axis.text.x = element_text(angle = 70, hjust = 1),
    plot.title = element_text(hjust = -1.2, size=18, face="bold")) -> p7

# NEW

# -
layout_matrix <- rbind(
  c(12, 12, 12, 12, 12, 12, 12, 12),
  c(NA, 8, 8, 9, 9, 9, 9, NA),
  c(10, 1, 1, 2, 2, 5, 5, NA), 
  c(10, 1, 1, 2, 2, 5, 5, NA), 
  c(10, 1, 1, 2, 2, 5, 5, NA), 
  c(10, 1, 1, 2, 2, 5, 5, 7), 
  c(11, 3, 3, 4, 4, 6, 6, 7),
  c(11, 3, 3, 4, 4, 6, 6, 7),
  c(11, 3, 3, 4, 4, 6, 6, 7),
  c(11, 3, 3, 4, 4, 6, 6, 7)
)

p8 <- textGrob("No homeostatsis")
p9 <- textGrob("Homeostatsis")
p10 <- textGrob("Synchrony")
p11 <- textGrob("Excitability")
p12 <- textGrob("Excitatory modulation")

@@

```{r, fig.width=4.5, fig.height=2.0}
shift <- -0.15
# 23 No H
# 21 w H
# 30 burst

@@

results202 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(mse_error), SD=sd(mse_error)) -> tmp2

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=mse_error, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8) +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), width=.15, size=0.2) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(title="a.", y="Variance (s)", x="Osc. rate (Hz)") +
  # lims(y=c(0, .15)) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.35, size=18, face="bold")) -> p1

@@

results203 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(mse_error), SD=sd(mse_error)) -> tmp2

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=mse_error, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8) +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), width=.15, size=0.2) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(title="b.", y="Variance (s)", x="Osc. rate (Hz)") +
  # lims(y=c(0, .15)) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.5, size=18, face="bold")) -> p2

@@

results207 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(mse_error), SD=sd(mse_error)) -> tmp2

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=mse_error, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05), color="dodgerblue3") +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8, color="dodgerblue3") +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), 
                width=.15, size=0.2, color="dodgerblue3") +
  labs(title="c.", y="Variance (s)", x="Osc. rate (Hz)") +
  theme_classic() + 
  # lims(y=c(0, .15)) +
  theme(plot.title = element_text(hjust = -.6, size=18, face="bold")) -> p5

@@

tmp5 <- rbind(tmp3, tmp4)
tmp5 %>% 
  ggplot(aes(x=osc_mode, y=rate_k - rate_ref, color=osc_mode)) +
  geom_point(size=-1, aes(fill=osc_mode)) +
  geom_boxplot(notch = TRUE, width=0.4,  outlier.size=0.05, outlier.alpha=0.5, show.legend=FALSE) +
  labs(title="f.", y=expression(Delta*" rate (Hz)"), x="") +
  theme_classic() +
  geom_hline(yintercept=0, size=0.2) +
  # lims(y=c(-3, 3)) +
  scale_fill_manual(values=c("dodgerblue3", "black"), name="Oscillation") +
  scale_color_manual(values=c("dodgerblue3", "black"), name="Oscillation") +
  stat_compare_means(method="wilcox.test", label="p.signif", 
                     label.x=1.3, size=3, show.legend=FALSE) +
  guides(fill = guide_legend(override.aes = list(shape = 15, size = 7, alpha=0.8))) +
  theme(
    legend.position = c(0.1, 2),
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.5, "cm"),
    axis.text.x = element_text(angle = 70, hjust = 1),
    plot.title = element_text(hjust = -1.2, size=18, face="bold")) -> p7

# NEW

# -
layout_matrix <- rbind(
  c(12, 12, 12, 12, 12, 12, 12, 12),
  c(NA, 8, 8, 9, 9, 9, 9, NA),
  c(10, 1, 1, 2, 2, 5, 5, NA), 
  c(10, 1, 1, 2, 2, 5, 5, NA), 
  c(10, 1, 1, 2, 2, 5, 5, NA), 
  c(10, 1, 1, 2, 2, 5, 5, 7), 
  c(11, 3, 3, 4, 4, 6, 6, 7),
  c(11, 3, 3, 4, 4, 6, 6, 7),
  c(11, 3, 3, 4, 4, 6, 6, 7),
  c(11, 3, 3, 4, 4, 6, 6, 7)
)

p8 <- textGrob("No homeostatsis")
p9 <- textGrob("Homeostatsis")
p10 <- textGrob("Synchrony")
p11 <- textGrob("Excitability")
p12 <- textGrob("Inhibitory modulation")

@@

```{r, fig.width=2.4, fig.height=1.7}
# -
# With H, E
# Var
results19 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate, Ca_target) %>% 
  summarise(M=mean(mse_error), SD=sd(mse_error)) -> tmp1

@@

# Rate
results19 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate, Ca_target) %>% 
  summarise(M=mean(rate_k - rate_ref), SD=sd(rate_k - rate_ref)) -> tmp2

>>>>

# -----------------------------------------------------------------------
# 15: Sustained E, with H
exp_code <- 201
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
stim_codes <- c(3)# , 4)

@@

# -----------------------------------------------------------------------
# 22: Sustained E, with NO H
exp_code <- 200
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
stim_codes <- c(3)#, 4)

@@

# -----------------------------------------------------------------------
# Calcium exp, E, sustained
exp_code <- 218
osc_codes <- c(105, 115, 125, 135, 145, 155)
osc_rates <- c(0.5, 1.5, 2.5, 3.5, 4.5, 5.5)
stim_codes <- c(3)

@@

results218 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    for(ca in ca_targets){
      o_c <- osc_codes[i]
      o_r <- osc_rates[i]

@@

      results218 <- rbind(results218, df)
    }
  }
}

# -----------------------------------------------------------------------
# # Add default Ca value, from exp
exp_code <- 211
osc_codes <- c(105, 115, 125, 135, 145, 155)
osc_rates <- c(0.5, 1.5, 2.5, 3.5, 4.5, 5.5)
stim_codes <- c(3)
ca_targets <- c(0.03, 0.03, 0.03, 0.03)

df <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    for(ca in ca_targets){

@@

      results218 <- rbind(results218, df)
    }
  }
}

@@

results200 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) -> tmp2

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=kappa_coord, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8) +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), width=.15, size=0.2) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(title="d.", y="Kappa", x="Osc. rate (Hz)") +
  # # lims(y=c(0, .15)) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.35, size=18, face="bold")) -> p1

@@

results201 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) -> tmp2

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=kappa_coord, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8) +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), width=.15, size=0.2) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(title="e.", y="Kappa", x="Osc. rate (Hz)") +
  # lims(y=c(0, .01)) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.5, size=18, face="bold")) -> p2

@@

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k - rate_ref, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8) +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), width=.15, size=0.2) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(title="a.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
  # lims(y=c(0, 70)) +
  geom_hline(yintercept=0, size=0.2) +
  theme_classic() + 
  theme(plot.title = element_text(hjust = -.25, size=18, face="bold")) -> p3

@@

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k - rate_ref, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8) +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), width=.15, size=0.2) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(title="b.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
  # lims(y=c(-4, 4)) +
  geom_hline(yintercept=0, size=0.2) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.3, size=18, face="bold")) -> p4

@@

results204 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) -> tmp2

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=kappa_coord, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05), color="dodgerblue3") +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8, color="dodgerblue3") +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), 
                width=.15, size=0.2, color="dodgerblue3") +
  labs(title="f.", y="Kappa", x="Osc. rate (Hz)") +
  theme_classic() + 
  # lims(y=c(0, .01)) +
  theme(plot.title = element_text(hjust = -.6, size=18, face="bold")) -> p5

@@

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k - rate_ref, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05), color="dodgerblue3") +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.6, color="dodgerblue3") +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), 
                width=.15, size=0.2, color="dodgerblue3") +
  geom_hline(yintercept=0, size=0.2) +
  labs(title="c.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
  # lims(y=c(-3, 3)) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.4, size=18, face="bold")) -> p6

@@

tmp5 <- rbind(tmp3, tmp4)
tmp5 %>% 
  ggplot(aes(x=osc_mode, y=rate_k - rate_ref, color=osc_mode)) +
  geom_point(size=-1, aes(fill=osc_mode)) +
  geom_boxplot(notch = TRUE, width=0.4,  outlier.size=0.05, outlier.alpha=0.5, show.legend=FALSE) +
  labs(title="g.", y=expression(Delta*" rate (Hz)"), x="") +
  theme_classic() +
  geom_hline(yintercept=0, size=0.2) +
  # lims(y=c(-3, 3)) +
  scale_fill_manual(values=c("dodgerblue3", "black"), name="Oscillation") +
  scale_color_manual(values=c("dodgerblue3", "black"), name="Oscillation") +
  stat_compare_means(method="wilcox.test", label="p.signif", 
                     label.x=1.3, size=3, show.legend=FALSE) +
  guides(fill = guide_legend(override.aes = list(shape = 15, size = 7, alpha=0.8))) +
  theme(
    legend.position = c(0.15, 2),
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.5, "cm"),
    axis.text.x = element_text(angle = 70, hjust = 1),
    plot.title = element_text(hjust = -1.2, size=18, face="bold")) -> p7

# -
layout_matrix <- rbind(
  c(12, 12, 12, 12, 12, 12, 12, 12),
  c(NA, 8, 8, 9, 9, 9, 9, NA),
  c(11, 3, 3, 4, 4, 6, 6, NA),
  c(11, 3, 3, 4, 4, 6, 6, NA),
  c(11, 3, 3, 4, 4, 6, 6, NA),
  c(11, 3, 3, 4, 4, 6, 6, 7),
  c(10, 1, 1, 2, 2, 5, 5, 7), 
  c(10, 1, 1, 2, 2, 5, 5, 7), 
  c(10, 1, 1, 2, 2, 5, 5, 7), 
  c(10, 1, 1, 2, 2, 5, 5, 7)

)

p8 <- textGrob("No homeostatsis")
p9 <- textGrob("Homeostatsis")
p10 <- textGrob("Coordination")
p11 <- textGrob("Excitability")
p12 <- textGrob("Excitatory modulation")

@@

```{r, fig.width=5, fig.height=2.25}
shift <- -0.15
# 23 No H
# 21 w H
# 30 burst

@@

results202 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) -> tmp2

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=kappa_coord, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8) +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), width=.15, size=0.2) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(title="d.", y="Kappa", x="Osc. rate (Hz)") +
  # lims(y=c(0, .15)) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.35, size=18, face="bold")) -> p1

@@

results203 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) -> tmp2

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=kappa_coord, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8) +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), width=.15, size=0.2) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(title="e.", y="Kappa", x="Osc. rate (Hz)") +
  # lims(y=c(0, .15)) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.5, size=18, face="bold")) -> p2

@@

results207 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) -> tmp2

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=kappa_coord, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05), color="dodgerblue3") +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8, color="dodgerblue3") +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), 
                width=.15, size=0.2, color="dodgerblue3") +
  labs(title="f.", y="Kappa", x="Osc. rate (Hz)") +
  theme_classic() + 
  # lims(y=c(0, .15)) +
  theme(plot.title = element_text(hjust = -.6, size=18, face="bold")) -> p5

@@

tmp5 <- rbind(tmp3, tmp4)
tmp5 %>% 
  ggplot(aes(x=osc_mode, y=rate_k - rate_ref, color=osc_mode)) +
  geom_point(size=-1, aes(fill=osc_mode)) +
  geom_boxplot(notch = TRUE, width=0.4,  outlier.size=0.05, outlier.alpha=0.5, show.legend=FALSE) +
  labs(title="g.", y=expression(Delta*" rate (Hz)"), x="") +
  theme_classic() +
  geom_hline(yintercept=0, size=0.2) +
  # lims(y=c(-3, 3)) +
  scale_fill_manual(values=c("dodgerblue3", "black"), name="Oscillation") +
  scale_color_manual(values=c("dodgerblue3", "black"), name="Oscillation") +
  stat_compare_means(method="wilcox.test", label="p.signif", 
                     label.x=1.3, size=3, show.legend=FALSE) +
  guides(fill = guide_legend(override.aes = list(shape = 15, size = 7, alpha=0.8))) +
  theme(
    legend.position = c(0.15, 2),
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.5, "cm"),
    axis.text.x = element_text(angle = 70, hjust = 1),
    plot.title = element_text(hjust = -1.2, size=18, face="bold")) -> p7

# -
layout_matrix <- rbind(
  c(12, 12, 12, 12, 12, 12, 12, 12),
  c(NA, 8, 8, 9, 9, 9, 9, NA),
  c(11, 3, 3, 4, 4, 6, 6, NA),
  c(11, 3, 3, 4, 4, 6, 6, NA),
  c(11, 3, 3, 4, 4, 6, 6, NA),
  c(11, 3, 3, 4, 4, 6, 6, 7),
  c(10, 1, 1, 2, 2, 5, 5, 7), 
  c(10, 1, 1, 2, 2, 5, 5, 7), 
  c(10, 1, 1, 2, 2, 5, 5, 7), 
  c(10, 1, 1, 2, 2, 5, 5, 7)
)

p8 <- textGrob("No homeostatsis")
p9 <- textGrob("Homeostatsis")
p10 <- textGrob("Coordination")
p11 <- textGrob("Excitability")
p12 <- textGrob("Inhibitory modulation")

@@

```{r, fig.width=2.4, fig.height=1.7}
# -
# With H, E
# Var
results218 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate, Ca_target) %>% 
  summarise(M=mean(kappa_coord - mse_ref), SD=sd(kappa_coord - mse_ref)) -> tmp1

@@

# Rate
results218 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate, Ca_target) %>% 
  summarise(M=mean(rate_k - rate_ref), SD=sd(rate_k - rate_ref)) -> tmp2
